### 2024-03-09 content/chapter_1.tex
:pencil: Update outline and contributions

\chapter{Introduction}
% \chapter{Summary of research problems and contribution}

@@

	Despite the great possibilities, the prototyping of \gls{ris} is still in its infancy and no commercial product has been released by the first quarter of 2024.
	The transition from theory to practice is hindered by many challenges, such as channel acquisition, response resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
	Most importantly, a comprehensive understanding of its potential is still missing and the precise role it shall play in 6G remains ambiguous.
	For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in space as a standalone device for \emph{channel shaping}.
	These applications have distinctive requirements and trade-offs, but they are not mutually exclusive and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
	Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
	Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
	To realize this vision, we need to:
	\begin{itemize}
		\item investigate the impact of \gls{ris} on various wireless applications and propose effective configurations for enhanced performance trade-off;
		\item compare the principles of \gls{ris} with other scatter-based technologies and develop a novel protocol for beamforming-modulation integration;
		\item rethink the architecture and modeling of \gls{ris} and explore its ultimate performance limits for further design evolution;
	\end{itemize}
	which are the motivations for Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} of this thesis, respectively.
\end{section}

\begin{section}{Objectives}

@@

\begin{section}{Publications}
\end{section}

>>>>

\chapter{Introduction}\label{ch:introduction}
% \chapter{Summary of research problems and contribution}

@@

	Despite the great possibilities, the prototyping of \gls{ris} is still in its infancy and no commercial product has been released by the first quarter of 2024.
	The transition from theory to practice is hindered by many challenges, such as channel acquisition, response resolution, out-of-band response mitigation, placement optimization, and integration with existing systems.
	Most importantly, a comprehensive understanding of its potential is still missing and the precise role it shall play in 6G remains ambiguous.
	For example, \gls{ris} could be incorporated into the transmitter and receiver for \emph{beamforming}, employed as a free-rider information source for \emph{modulation}, or placed in space as a standalone device for \emph{channel shaping}.
	These applications have distinctive requirements and trade-offs, but they are not mutually exclusive and may be evolved into a versatile tool, which blurs the boundary between the network and environment.
	Imagine a future where everything can be ``smartened'' by coating with a metamaterial layer and attaching a microcontroller tag.
	Only a few electromagnetic sources are needed, while most objects can exploit the surrounding waves to energize themselves, sense the environment, communicate with others, and help those in need when idle.
	This vision motivates us to explore the fundamental limits of \gls{ris} and integrate it with state-of-the-art wireless technologies.
	% In particular, Chapters \ref{ch:ris_aided_swipt}--\ref{ch:channel_shaping} respectively aim to:
	% \begin{itemize}
	% 	\item Investigate the impact of \gls{ris} on wireless information and power transfer and propose effective configurations for enhanced performance trade-off;
	% 	\item Compare the principles of \gls{ris} with various backscatter applications and develop a novel protocol for beamforming-modulation integration;
	% 	\item Rethink the architecture and modeling of \gls{ris} and characterize its ultimate channel shaping capabilities for further design reference.
	% \end{itemize}
\end{section}

% \begin{section}{Summary of Contributions}
% 	The key contributions of Chapter \ref{ch:ris_aided_swipt} are summarized as follows:
% 	\begin{itemize}
% 		\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with different receiver architectures;
% 		\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
% 		\item Characterize the \gls{r-e} performance trade-off by maximizing harvested energy subject to different communication rate constraints;
% 		\item Propose local-optimal and low-complexity algorithms and evaluate their narrow and wideband performance through numerical simulations;
% 		\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
% 	\end{itemize}

% 	The key contributions of Chapter \ref{ch:riscatter} are summarized as follows:
% 	\begin{itemize}
% 		\item Compare \gls{ris} with state-of-the-art \gls{bc} technologies and discuss the key properties of active and passive transmissions coexisting systems;
% 		\item Unify \gls{ris} and \gls{bc} as one battery-free cognitive radio called RIScatter, where dispersed or co-located scatter nodes ride over an active primary link to modulate their own information and engineering the legacy channel simultaneously;
% 		\item Integrate backscatter modulation and passive beamforming seamlessly into the input distribution design that allows arbitrary trade-off in between;
% 		\item Propose a low-complexity cooperative receiver that sequentially decodes both coexisting links and exploits backscatter detection as part of channel training;
% 		\item Characterize the achievable primary-backscatter rate region over different designs of input distribution at the scatter nodes, active beamforming at the \gls{ap}, and energy detector at the receiver;
% 		\item Discuss the impact of practical factors such as the number of scatter nodes and states, transmit antenna size, backscatter symbol duration, and \gls{snr} on the system performance.
% 	\end{itemize}

% 	The key contributions of Chapter \ref{ch:channel_shaping} are summarized as follows:
% 	\begin{itemize}
% 		\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
% 		\item Focus on a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior signal processing performance (subspace alignment and subchannel rearrangement) over the widely-adopted diagonal model;
% 		\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
% 		\item Characterize the Pareto frontiers of channel singular values and obtain power- and rate-optimal \gls{bd}-\gls{ris} configurations in \gls{mimo} \gls{pc};
% 		\item Investigate the impact of \gls{bd}-\gls{ris} on leakage interference suppression and \gls{wsr} maximization in \gls{mimo} \gls{ic};
% 		\item Discuss how channel shaping helps to decouple joint \gls{ris}-transceiver designs with comparable performance and significantly reduced complexity.
% 	\end{itemize}
% \end{section}
	The thesis is outlined as follows:
	\begin{itemize}
		\item Chapter \ref{ch:introduction} introduces \gls{ris} as a promising technology for ambient wave redirection and highlights its potential benefits in future wireless networks. It discusses the motivation, objectives, and contributions of each research chapter. A list of publications is also provided.
		\item Chapter \ref{ch:background} provides the necessary background knowledge for the subsequent chapters, including the fundamental concepts, operating principles, hardware implementation, signal and system models, performance metrics, and design challenges for \gls{ris}, \gls{wpt}, \gls{swipt}, \gls{bc}, and \gls{mimo} systems. It also reviews the state-of-the-art research in relevant topics and raise critical questions to be addressed in the following chapters.
		\item Chapter \ref{ch:ris_aided_swipt} investigate the impact of \gls{ris} on wireless information and power transfer. The key contributions include:
		\begin{itemize}
			\item Introduce \gls{ris} to a multi-antenna multi-carrier \gls{swipt} system with different receiver architectures;
			\item Consider joint waveform and beamforming design for the proposed system under a practical energy harvester model;
			\item Characterize the \gls{r-e} performance trade-off by maximizing harvested energy subject to different communication rate constraints;
			\item Propose local-optimal and low-complexity algorithms and evaluate their narrow and wideband performance through numerical simulations;
			\item Discuss the array gain for communication and the scaling order for power transfer in terms of the number of transmit antennas and \gls{ris} elements.
		\end{itemize}
		\item Chapter \ref{ch:riscatter} develops a novel scatter protocol that integrates beamforming and modulation. The key contributions include:
		\begin{itemize}
			\item Provide an in-depth comparison of \gls{ris} with state-of-the-art \gls{bc} technologies and discuss the key properties of active and passive transmissions coexisting systems;
			\item Unify \gls{ris} and \gls{bc} as one battery-free cognitive radio called RIScatter, where dispersed or co-located scatter nodes ride over an active primary link to modulate their own information and engineering the legacy channel simultaneously;
			\item Integrate backscatter modulation and passive beamforming seamlessly into the input distribution design that allows arbitrary trade-off in between;
			\item Propose a low-complexity cooperative receiver that sequentially decodes both coexisting links and exploits backscatter detection as part of channel training;
			\item Characterize the achievable primary-backscatter rate region over different designs of input distribution at the scatter nodes, active beamforming at the \gls{ap}, and energy detector at the receiver;
			\item Discuss the impact of practical factors such as the number of scatter nodes and states, transmit antenna size, backscatter symbol duration, and \gls{snr} on the system performance.
		\end{itemize}
		\item Chapter \ref{ch:channel_shaping} explores the ultimate channel shaping capabilities of \gls{ris} in \gls{mimo} systems. The key contributions include:
		\begin{itemize}
			\item Quantify the capability of a passive \gls{ris} to reshape the \gls{mimo} \gls{pc} in terms of singular values via analytical bounds and numerical optimization;
			\item Focus on a general \gls{bd}-\gls{ris} architecture featuring element-wise connections and demonstrate its superior signal processing performance (subspace alignment and subchannel rearrangement) over the widely-adopted diagonal model;
			\item Propose an efficient \gls{rcg} algorithm for general \gls{bd}-\gls{ris} optimization and provide low-complexity solutions for quadratic problems;
			\item Characterize the Pareto frontiers of channel singular values and obtain power- and rate-optimal \gls{bd}-\gls{ris} configurations in \gls{mimo} \gls{pc};
			\item Investigate the impact of \gls{bd}-\gls{ris} on leakage interference suppression and \gls{wsr} maximization in \gls{mimo} \gls{ic};
			\item Discuss how channel shaping helps to decouple joint \gls{ris}-transceiver designs with comparable performance and significantly reduced complexity.
		\end{itemize}
	\end{itemize}

@@

\begin{section}{Publications}
	\begin{itemize}
		\item \bibentry{Zhao2022}
		\item \bibentry{Zhao2022a}
		\item \bibentry{Zhao2023}
		\item \bibentry{Zhao2024}
	\end{itemize}
\end{section}
